A Linked Open Social Dataset for Scientific Benchmarking

### 2019-06-20 misc/overallText.tex
finished a first version of the main document
adiantado um pouco do artigo

Database consists of 37467423 triples, 3088219 edges yield by interactions or relations, 382735 participants and 229008584 characters. Among all snapshots, 63 are ego snapshots, 53 are group snapshots; 45 have interaction edges, 89 have friendship edges; 42 have text content from messages.

>>>>

The database consists of 34,120,026 triples, 3,172,927 network links yield by selected interactions or relations, 382,568 participants and 253,155,020 characters in text data. Among all snapshots, 63 are ego snapshots, 54 are group snapshots; 49 have network interaction links, 89 have network friendship links; 43 have text content from messages.
